Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{3mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-3mm}}

@@

\extraspacing \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\contained_{R_{k-2}}(\bm{t}) = \contained_{R_{k-2}}(h^*)$. We can then derive 
\myeqn{
    && \sum_{h^* \in H^*} |\contained_{R_{k-2}}(h^*)|  \nn \\ 
    &\le& \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\contained_{R_{k-2}}(\bm{t})| 
    \leq \out \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

@@

As mentioned in Section~\ref{sec:intro:prev}, 2-SJ can be solved in $F_2(n, \out) = O(n \log n + \out)$ time using a comparison-based algorithm. By Theorem~\ref{thm:main-recur}, in general, a comparison-based $(k-1)$-SJ algorithm with runtime $F_{k-1}(n, \out)$ spawns a comparison-based $k$-SJ algorithm whose running time $F_k(n, \out)$ obeys \eqref{eqn:main:reccurrence}. Specifically, for $k \ge 3$, there is a constant $c \ge 2$ such that
\myeqn{
    && F_{k}(n, \out) \nn \\
    &\le& c \cdot k^3 \cdot \big( F_{k-1}(n, \out) + n \log n + k \cdot \out \big) \nn \\
    &=& c^2 \cdot k^3(k-1)^3 \cdot (F_{k-2}(n,\out) + n\log n + k\cdot \out) + \nn \\
    && c \cdot k^3 \cdot (n\log n + k\cdot \out ) \nn\\
    &<& c^2 \cdot k^3(k-1)^3 \cdot F_{k-2}(n,\out) +  \nn\\
    && (c+c^2)\cdot k^3(k-1)^3 \cdot (n\log n + k \cdot\out) \nn \\
    &\leq& c^3 \cdot k^3(k-1)^3(k-2)^3 \cdot F_{k-3}(n,\out) + \nn\\
    && (c+c^2+c^3)\cdot k^3(k-1)^3(k-2)^3 \cdot (n\log n + k \cdot\out) \nn\\
    &\leq& ... \nn \\
    &\leq& c^{k-2} \cdot (k!)^3 \cdot F_{2}(n,\out) + \nn \\
    && \Big(\sum_{i =1}^{k-2}c^i \Big)\cdot (k!)^3 \cdot (n\log n + k \cdot\out) \nn \\
    &\leq & 2c^{k-1} \cdot (k!)^3 \cdot O(n\log n + k \cdot\out) \nn
}
which completes the proof of Theorem~\ref{thm:main-alg}.

>>>>

\def\vgap{\vspace{1mm}}
\def\extraspacing{\vspace{2mm} \noindent}
\def\figcapup{\vspace{-2mm}}
\def\figcapdown{\vspace{-3mm}}

@@

\extraspacing \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\contained_{R_{k-2}}(\bm{t}) = \contained_{R_{k-2}}(h^*)$. We can then derive 
\myeqn{
    \sum_{h^* \in H^*} |\contained_{R_{k-2}}(h^*)|
    \le
    \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\contained_{R_{k-2}}(\bm{t})|
    \leq \out \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

@@

As mentioned in Section~\ref{sec:intro:prev}, 2-SJ can be solved in $F_2(n, \out) = O(n \log n + \out)$ time using a comparison-based algorithm. By Theorem~\ref{thm:main-recur}, in general, a comparison-based $(k-1)$-SJ algorithm with runtime $F_{k-1}(n, \out)$ spawns a comparison-based $k$-SJ algorithm whose running time $F_k(n, \out)$ obeys \eqref{eqn:main:reccurrence}. Specifically, for $k \ge 3$, there is a constant $c \ge 2$ such that
\myeqn{
    && F_{k}(n, \out) \nn \\
    &\le& c \cdot k^3 \cdot \big( F_{k-1}(n, \out) + n \log n + k \cdot \out \big) \nn \\
    &=& c^2 \cdot k^3(k-1)^3 \cdot (F_{k-2}(n,\out) + n\log n + k\cdot \out) + c \cdot k^3 \cdot (n\log n + k\cdot \out ) \nn\\
    &<& c^2 \cdot k^3(k-1)^3 \cdot F_{k-2}(n,\out) +  (c+c^2)\cdot k^3(k-1)^3 \cdot (n\log n + k \cdot\out) \nn \\
    &\leq& c^3 \cdot k^3(k-1)^3(k-2)^3 \cdot F_{k-3}(n,\out) +
    (c+c^2+c^3)\cdot k^3(k-1)^3(k-2)^3 \cdot (n\log n + k \cdot\out) \nn\\
    &\leq& ... \nn \\
    &\leq& c^{k-2} \cdot (k!)^3 \cdot F_{2}(n,\out) + \Big(\sum_{i =1}^{k-2}c^i \Big)\cdot (k!)^3 \cdot (n\log n + k \cdot\out) \nn \\
    &\leq & 2c^{k-1} \cdot (k!)^3 \cdot O(n\log n + k \cdot\out) \nn
}
which completes the proof of Theorem~\ref{thm:main-alg}.
